gij bent 2

### 2025-08-20 paper/paper.qmd
references added

Linguistically, the effects of networks have been studied before. Milroy and Milroy [1985 TODO], who base themselves on Granovetter [1973 TODO] and Rogers and Shoemaker [1971 TODO], demonstrated that in a network both weak and strong ties are essential for the propagation of linguistic change. Strong ties (e.g. close friends and family) maintain and reinforce linguistic norms within tight-knit groups, resisting linguistic innovation. In contrast, weak ties (e.g. acquaintances) form bridges between groups, facilitate the spread of linguistic innovations. Weak ties are especially crucial for exposing individuals to linguistic features or patterns that are not present within their immediate, tightly connected group, enabling the flow of new linguistic forms across disparate groups, broadening the reach of linguistic innovations. Once exposed to these new forms, individuals connected through weak ties may adopt them and, through their strong ties, introduce them to their close-knit circles.

>>>>

Linguistically, the effects of networks have been studied before. @milroy_linguistic_1985, who base themselves on @granovetter_strength_1973 and @rogers_communication_1971, demonstrated that in a network both weak and strong ties are essential for the propagation of linguistic change. Strong ties (e.g. close friends and family) maintain and reinforce linguistic norms within tight-knit groups, resisting linguistic innovation. In contrast, weak ties (e.g. acquaintances) form bridges between groups, facilitate the spread of linguistic innovations. Weak ties are especially crucial for exposing individuals to linguistic features or patterns that are not present within their immediate, tightly connected group, enabling the flow of new linguistic forms across disparate groups, broadening the reach of linguistic innovations. Once exposed to these new forms, individuals connected through weak ties may adopt them and, through their strong ties, introduce them to their close-knit circles.
